Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-08-21 paper/paper.tex
feat: set updated link for tag

We now study the packaging of all components of the preCICE ecosystem one by one, including challenges, solutions, and workarounds.
We first look at preCICE itself, followed by additional tooling and bindings.
Afterwards, we study all solvers and their respected adapters.
Next, we show that Nix can also be used to generate iso files as well as qemu and Vagrant VM images. Finally, we try running all preCICE tutorials.
The Nix code for all components is available online\footnote{\url{https://github.com/precice/nix-packages/releases/tag/deRSE24-paper-submission}} and can be used to download and run any of the presented packages.

>>>>

We now study the packaging of all components of the preCICE ecosystem one by one, including challenges, solutions, and workarounds.
We first look at preCICE itself, followed by additional tooling and bindings.
Afterwards, we study all solvers and their respected adapters.
Next, we show that Nix can also be used to generate iso files as well as qemu and Vagrant VM images. Finally, we try running all preCICE tutorials.
The Nix code for all components is available online\footnote{\url{https://github.com/precice/nix-packages/releases/tag/deRSE24-paper-submission-v2}} and can be used to download and run any of the presented packages.
